---
title: "r data exploration"
author: "Jordan Sibley"
format: html
editor: visual
---

## Instructions 
- Set up your local and remote git repo by running usethis::use_git() and then usethis::use_github()

- Attach the {tidyverse}, {skimr}, and {GGally} packages in the setup code chunk
```{r}
library(tidyverse)
library(skimr)
library(GGally)
```

- Run View(diamonds) in the Console to look at the built-in diamonds data set in R

- Explore the data set using the functions names(), dim(), summary(), head(), tail(), and skimr::skim()
```{r}
# exploring data 
names(diamonds)

dim(diamonds)

summary(diamonds)

head(diamonds)

tail(diamonds)

skimr::skim(diamonds)
```

- Create a pairs plot using ggpairs()
```{r}
GGally::ggpairs(diamonds)
```

- Create a basic ggplot scatterplot of diamond price (price) as a function of size (carat)

```{r}
ggplot(data = diamonds, aes(x = price, y = carat))+
  geom_point()
```

- Create a histogram showing the distribution of values in the carat column (recall: a histogram only requires a single variable, e.g. aes(x = carat))

```{r}
ggplot(data = diamonds, aes(x = carat))+
  geom_histogram()
```

- Save, stage, commit, pull, then push your changes back to your repo in RStudio using the GUI interface (buttons)


- Create a boxplot (see: geom_boxplot) of diamond clarity (on the x-axis) and price (y-axis).
In the command line, stage, commit, & push changes


